---
title: "EPG Data analysis"
author: "Daniel Kunk"
date: "2/10/2022"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T,
                      results = "hide")
```

# EPG Statistical Analysis Code Package. 
### This code was designed to preform statistical analysis on a csv file output from the Serrea Workbook. Please see .readme file to understand how to set up the .csv file so that it can be compatible with this code. 
```{r}
# loading the .csv file output. This file is designed off the output from the Serrea EPG workbook. 
# assigning the csv file to a data frame called epgdata. 
epgdata = read.csv('C:/Users/danie/Desktop/NALAM LAB/EPG/EPG ANALYSIS/24_LD_EPG DATA/DKVERSION_24hr_LD_EPGDATA .csv')
epgdata
```


```{r}
# Running all of the K.W tests for each parameter across all light treatments using a For Loop. 
indices <- 3:121
kruskal_results_list <- vector('list', length = length(indices))
for (i in 3:121) {
  
  kruskal_results_list[[i-2]] <- tryCatch({
    kruskal.test(
      x = epgdata[,i],
      g = epgdata[,2],
      na.action = na.omit
    )
    
  }, error = function(e) {
    cat('Column ', i, ' did not run.')
  return(e)
    } 
  )
}

#Output of all the K.W. tests into a list called kruskal results list. 
for (i in 1:119) {
  cat('Column ', i+2, ': \n')
print(kruskal_results_list[[i]])
}

#
p_val_dat <- data.frame(
  column_num = 3:121,
  p_vals = rep(0, 119)
)

for (i in 1:119) {
  if (!is.null(kruskal_results_list[[i]]$p.value)) {
    p_val_dat$p_vals[i] <- kruskal_results_list[[i]]$p.value
  } else {
    p_val_dat$p_vals[i] <- NA
  }
}
p_val_dat$col_names = colnames(epgdata[3:121])
# The code below that has been hashtagged out will save the p-value data frame to the file location of choice. This file will list all the statistically significant waveforms from the K.W. tests. 
#write.csv(p_val_dat,"C:/Users/danie/Desktop/NALAM LAB/EPG/EPG ANALYSIS/24_LD_EPG DATA/p_values_24hrLD_4hr_kruskalwallis.csv", row.names = FALSE)
```


              
### The code below shows the same process except a different datatable with only two treatments, day and night, was used.
              
```{r}
epgdata_dvn = read.csv('C:/Users/danie/Desktop/NALAM LAB/EPG/EPG ANALYSIS/24_LD_EPG DATA/DKVERSION_DvN_LD_EPGDATA .csv')

indices <- 3:121
kruskal_results_list_dvn <- vector('list', length = length(indices))
for (i in 3:121) {
  
  kruskal_results_list_dvn[[i-2]] <- tryCatch({
    kruskal.test(
      x = epgdata_dvn[,i],
      g = epgdata_dvn[,2],
      na.action = na.omit
    )
    
  }, error = function(e) {
    cat('Column ', i, ' did not run.')
  return(e)
    } 
  )
}
#Output of all the K.W. tests into a list called kruskal results list. 
for (i in 1:119) {
  cat('Column ', i+2, ': \n')
print(kruskal_results_list_dvn[[i]])
}

#
p_val_dat_dvn <- data.frame(
  column_num = 3:121,
  p_vals = rep(0, 119)
)

for (i in 1:119) {
  if (!is.null(kruskal_results_list_dvn[[i]]$p.value)) {
    p_val_dat_dvn$p_vals[i] <- kruskal_results_list_dvn[[i]]$p.value
  } else {
    p_val_dat_dvn$p_vals[i] <- NA
  }
}
p_val_dat_dvn$col_names = colnames(epgdata_dvn[3:121])

write.csv(p_val_dat_dvn,"C:/Users/danie/Desktop/NALAM LAB/EPG/EPG ANALYSIS/24_LD_EPG DATA/p_values_DvN_4hr_kruskalwallis.csv", row.names = FALSE)

```


### Only a pairwise wilcoxon test is neccesary here because we are only comparing two groups. 
```{r}
#running all of the pariwise wilcoxon rank sum tests: correcting using bonferroni, but other corrections might be more useful. 
indices <- 3:121
multcomp_results_list <- vector('list', length = length(indices))
for (i in 3:121) {
  
  multcomp_results_list[[i-2]] <- tryCatch({
    pairwise.wilcox.test(
      x = epgdata[,i],
      g = epgdata[,2],
      na.action = na.omit
    )
    
  }, error = function(e) {
    cat('Column ', i, ' did not run.')
  return(e)
    } 
  )
}

#Output of all the pariwise wilcoxon tests into a list called multcomp results list. 
for (i in 1:119) {
  cat('Column ', i+2, ': \n')
print(multcomp_results_list[[i]])
}

#binding p-values to data frame 
multcomp_dat <- data.frame(
  column_num = 3:121,
  p_vals = rep(0, 119)
)

for (i in 1:119) {
  if (!is.null(multcomp_results_list[[i]]$p.value)) {
    multcomp_dat$p_vals[i] <- multcomp_results_list[[i]]$p.value
  } else {
    multcomp_dat$p_vals[i] <- NA
  }
}
multcomp_dat$col_names = colnames(epgdata[3:121])

```




